---
title: "Soccer Transfer Market EDA"
author: "Dowon Kim"
date: "2026-04-06"
output: html_document
---

## 패키지 로드 및 데이터 불러오기

```{r setup, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(ggrepel)
library(patchwork)
library(corrplot)

clean_data <- read_csv("clean_data.csv")

# -----------------------------------------------
# 포지션 세분화 매핑 (sub_position → 6개 그룹)
# -----------------------------------------------
clean_data <- clean_data %>%
  mutate(
    pos_group = case_when(
      sub_position == "Goalkeeper"                                  ~ "GK",
      sub_position == "Centre-Back"                                 ~ "CB",
      sub_position %in% c("Left-Back", "Right-Back")               ~ "SB",
      sub_position %in% c("Central Midfield", "Defensive Midfield",
                           "Right Midfield", "Left Midfield")       ~ "CM/DM",
      sub_position %in% c("Attacking Midfield", "Second Striker")   ~ "AM",
      sub_position %in% c("Centre-Forward", "Right Winger",
                           "Left Winger")                           ~ "FW",
      TRUE ~ "Other"
    ),
    pos_group = factor(pos_group,
                       levels = c("FW","AM","CM/DM","SB","CB","GK")),
    # npxG per 90 계산
    npxG_per90 = npxG_Expected / Mins_Per_90_Playing
  )

# -----------------------------------------------
# 리그 라벨
# -----------------------------------------------
league_labels <- c(
  "GB1" = "EPL",
  "ES1" = "La Liga",
  "L1"  = "Bundesliga",
  "IT1" = "Serie A",
  "FR1" = "Ligue 1"
)

clean_data <- clean_data %>%
  mutate(
    to_league_label   = league_labels[to_league],
    from_league_label = league_labels[from_league],
    U21_label         = ifelse(U21_dummy == 1, "U21 (Youth)", "General"),
    # [v5.0 신규] O30 라벨
    O30_label         = ifelse(O30_dummy == 1, "O30 (Veteran)", "Under 30"),
    league_diff_label = case_when(
      league_level_diff ==  1 ~ "Lower to Higher",
      league_level_diff ==  0 ~ "Same Level",
      league_level_diff == -1 ~ "Higher to Lower",
      TRUE ~ "Unknown"
    )
  )

# 색상 팔레트
pos_colors <- c(
  "FW"    = "#e6550d",
  "AM"    = "#fd8d3c",
  "CM/DM" = "#3182bd",
  "SB"    = "#74c476",
  "CB"    = "#31a354",
  "GK"    = "#756bb1"
)

league_colors <- c(
  "EPL"        = "#e6550d",
  "La Liga"    = "#3182bd",
  "Bundesliga" = "#31a354",
  "Serie A"    = "#756bb1",
  "Ligue 1"    = "#fd8d3c"
)
```

---

## Graph 1. Key Variable Distributions

```{r fig.width=14, fig.height=10, message=FALSE, warning=FALSE}
p1a <- ggplot(clean_data, aes(x = transfer_fee_raw)) +
  geom_histogram(bins = 50, fill = "#3182bd", color = "white", alpha = 0.85) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Transfer Fee Distribution (Raw)",
       subtitle = "Highly right-skewed — most transfers cluster at lower values",
       x = "Transfer Fee (EUR)", y = "Count") +
  theme_minimal(base_size = 11)

p1b <- ggplot(clean_data, aes(x = log_transfer_fee)) +
  geom_histogram(bins = 50, fill = "#e6550d", color = "white", alpha = 0.85) +
  labs(title = "Transfer Fee Distribution (Log Transformed)",
       subtitle = "Approximately normal after log transformation",
       x = "log(Transfer Fee)", y = "Count") +
  theme_minimal(base_size = 11)

p1c <- ggplot(clean_data %>% filter(pos_group != "GK"),
              aes(x = xG_Per)) +
  geom_histogram(bins = 40, fill = "#756bb1", color = "white", alpha = 0.85) +
  labs(title = "xG per 90 Distribution",
       subtitle = "Outfield players only (GK excluded)",
       x = "xG per 90", y = "Count") +
  theme_minimal(base_size = 11)

p1d <- ggplot(clean_data %>% filter(pos_group != "GK"),
              aes(x = npxG_per90)) +
  geom_histogram(bins = 40, fill = "#31a354", color = "white", alpha = 0.85) +
  labs(title = "npxG per 90 Distribution",
       subtitle = "Non-penalty xG — removes penalty bias",
       x = "npxG per 90", y = "Count") +
  theme_minimal(base_size = 11)

(p1a + p1b) / (p1c + p1d)
```

---

## Graph 2. xG per 90 vs log(Transfer Fee) by Position

```{r fig.width=11, fig.height=7, message=FALSE, warning=FALSE}
ggplot(
  clean_data %>% filter(pos_group != "GK"),
  aes(x = xG_Per, y = log_transfer_fee,
      color = pos_group, size = age_at_transfer)
) +
  geom_point(alpha = 0.4) +
  geom_smooth(aes(group = pos_group), method = "lm",
              se = FALSE, linewidth = 1.1, show.legend = FALSE) +
  scale_color_manual(values = pos_colors) +
  scale_size_continuous(range = c(1, 4), name = "Age") +
  labs(
    title    = "xG per 90 vs log(Transfer Fee) by Position",
    subtitle = "Goalkeepers excluded — xG not applicable for GK",
    x        = "xG per 90",
    y        = "log(Transfer Fee)",
    color    = "Position Group"
  ) +
  theme_minimal(base_size = 12) +
  guides(size  = guide_legend(order = 2),
         color = guide_legend(order = 1))
```

---

## Graph 3. Transfer Fee Distribution by Position (Sub-position)

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
ggplot(clean_data,
       aes(x = pos_group, y = log_transfer_fee, fill = pos_group)) +
  geom_boxplot(alpha = 0.85, outlier.alpha = 0.25, outlier.size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 18,
               size = 3, color = "black", show.legend = FALSE) +
  scale_fill_manual(values = pos_colors) +
  labs(
    title    = "Transfer Fee Distribution by Position Group",
    subtitle = "Diamond = Mean  |  Line = Median  |  FW/AM command highest premiums",
    x        = "Position Group",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")
```

---

## Graph 4. Transfer Fee Distribution by League

```{r fig.width=11, fig.height=6, message=FALSE, warning=FALSE}
ggplot(clean_data,
       aes(x = reorder(to_league_label, log_transfer_fee, median),
           y = log_transfer_fee,
           fill = to_league_label)) +
  geom_boxplot(alpha = 0.85, outlier.alpha = 0.25, outlier.size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 18,
               size = 3, color = "black", show.legend = FALSE) +
  scale_fill_manual(values = league_colors) +
  labs(
    title    = "Transfer Fee Distribution by League",
    subtitle = "EPL commands significantly higher fees — sorted by median",
    x        = "League",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")
```

---

## Graph 5. League Difficulty (UEFA Coefficient) vs Transfer Fee

```{r fig.width=13, fig.height=6, message=FALSE, warning=FALSE}
p5a <- ggplot(clean_data %>% filter(!is.na(from_league_label)),
              aes(x = UEFA_coeff_from, y = log_transfer_fee,
                  color = from_league_label)) +
  geom_point(alpha = 0.35, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE,
              color = "black", linewidth = 1.2, linetype = "dashed") +
  scale_color_manual(values = league_colors) +
  labs(
    title    = "Origin League UEFA Coefficient vs log(Transfer Fee)",
    subtitle = "Does playing in a stronger league command higher fees?",
    x        = "UEFA Coefficient (Origin League)",
    y        = "log(Transfer Fee)",
    color    = "Origin League"
  ) +
  theme_minimal(base_size = 11)

p5b <- ggplot(clean_data,
              aes(x = factor(league_diff_label,
                             levels = c("Lower to Higher",
                                        "Same Level",
                                        "Higher to Lower")),
                  y = log_transfer_fee,
                  fill = factor(league_diff_label,
                                levels = c("Lower to Higher",
                                           "Same Level",
                                           "Higher to Lower")))) +
  geom_boxplot(alpha = 0.85, outlier.alpha = 0.25) +
  scale_fill_manual(values = c("Lower to Higher" = "#e6550d",
                                "Same Level"       = "#3182bd",
                                "Higher to Lower"  = "#31a354")) +
  labs(
    title    = "Transfer Fee by League Movement Direction",
    subtitle = "Moving to a higher-level league commands a premium?",
    x        = "Transfer Direction",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

p5a + p5b
```

---

## Graph 6. U21 Youth Premium

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
p6a <- ggplot(clean_data,
              aes(x = U21_label, y = log_transfer_fee, fill = U21_label)) +
  geom_boxplot(alpha = 0.85, outlier.alpha = 0.25) +
  stat_summary(fun = mean, geom = "point", shape = 18,
               size = 3, color = "black", show.legend = FALSE) +
  scale_fill_manual(values = c("U21 (Youth)" = "#e6550d",
                                "General"     = "#3182bd")) +
  labs(
    title    = "Transfer Fee: U21 Youth vs General Players",
    subtitle = paste0("U21 n=", sum(clean_data$U21_dummy == 1),
                      "  |  General n=", sum(clean_data$U21_dummy == 0)),
    x        = "Player Type",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

p6b <- ggplot(clean_data,
              aes(x = U21_label, y = log_transfer_fee, fill = U21_label)) +
  geom_violin(alpha = 0.7, trim = FALSE) +
  geom_boxplot(width = 0.15, fill = "white", alpha = 0.8) +
  scale_fill_manual(values = c("U21 (Youth)" = "#e6550d",
                                "General"     = "#3182bd")) +
  labs(
    title    = "Transfer Fee Distribution: U21 vs General (Violin)",
    subtitle = "Violin shows full distribution shape",
    x        = "Player Type",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

p6a + p6b
```

---

## Graph 7. COVID Season Impact

```{r fig.width=11, fig.height=6, message=FALSE, warning=FALSE}
season_avg <- clean_data %>%
  group_by(transfer_season, covid_dummy) %>%
  summarise(
    avg_fee    = mean(transfer_fee_raw, na.rm = TRUE),
    median_fee = median(transfer_fee_raw, na.rm = TRUE),
    n          = n(),
    .groups    = "drop"
  )

ggplot(season_avg,
       aes(x = transfer_season, y = avg_fee / 1e6,
           fill = factor(covid_dummy))) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = paste0("n=", n)),
            vjust = -0.5, size = 3.2, fontface = "bold") +
  geom_hline(yintercept = mean(season_avg$avg_fee) / 1e6,
             linetype = "dashed", color = "gray40", linewidth = 0.8) +
  scale_fill_manual(values = c("0" = "#3182bd", "1" = "#e6550d"),
                    labels = c("0" = "Normal Season",
                               "1" = "COVID Season")) +
  labs(
    title    = "Average Transfer Fee by Season — COVID Impact",
    subtitle = "Red = COVID seasons  |  Dashed line = overall average",
    x        = "Season",
    y        = "Average Fee (Million EUR)",
    fill     = "Season Type"
  ) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

---

## Graph 8. Age vs log(Transfer Fee) — Quadratic Fit + U21/O30 Cutoff Lines
### [v5.0 수정] 만 21세(U21 기준), 만 30세(O30 기준) 수직 기준선 추가

```{r fig.width=13, fig.height=6, message=FALSE, warning=FALSE}
# 피크 나이 계산 (전체 데이터 2차 회귀에서 꼭짓점 계산)
lm_age <- lm(log_transfer_fee ~ age_at_transfer + age_squared,
             data = clean_data)
peak_age <- -coef(lm_age)[2] / (2 * coef(lm_age)[3])

p8a <- ggplot(clean_data,
              aes(x = age_at_transfer, y = log_transfer_fee)) +
  geom_point(alpha = 0.20, size = 1.3, color = "#7f8c8d") +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x^2),
              color   = "#2980b9",
              linewidth = 1.3,
              se = TRUE,
              fill = "#aed6f1",
              alpha = 0.25) +
  # [v5.0] U21 수직 기준선
  geom_vline(xintercept = 21,
             color    = "#27ae60",
             linetype = "dashed",
             linewidth = 0.9) +
  # [v5.0] O30 수직 기준선
  geom_vline(xintercept = 30,
             color    = "#e74c3c",
             linetype = "dashed",
             linewidth = 0.9) +
  annotate("text",
           x = 21.4,
           y = max(clean_data$log_transfer_fee, na.rm = TRUE) * 0.97,
           label = "Age 21\n(U21 cutoff)",
           color = "#27ae60", hjust = 0, size = 3.2, fontface = "bold") +
  annotate("text",
           x = 30.4,
           y = max(clean_data$log_transfer_fee, na.rm = TRUE) * 0.97,
           label = "Age 30\n(O30 cutoff)",
           color = "#e74c3c", hjust = 0, size = 3.2, fontface = "bold") +
  annotate("text",
           x = round(peak_age, 1), y = 1.2,
           label = paste0("Peak ~Age ", round(peak_age, 1)),
           color = "#2c3e50", size = 3.0, fontface = "italic") +
  labs(
    title    = "Age vs log(Transfer Fee) — Quadratic Fit with U21 and O30 Thresholds",
    subtitle = "Green dashed = U21 dummy cutoff (age 21)  |  Red dashed = O30 dummy cutoff (age 30)",
    x        = "Age at Transfer (completed years)",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 11)

p8b <- ggplot(clean_data %>% filter(pos_group != "Other"),
              aes(x = age_at_transfer, y = log_transfer_fee,
                  color = pos_group)) +
  geom_smooth(method = "lm",
              formula = y ~ x + I(x^2),
              se = FALSE, linewidth = 1.1) +
  geom_vline(xintercept = 21, color = "#27ae60",
             linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 30, color = "#e74c3c",
             linetype = "dashed", linewidth = 0.7) +
  scale_color_manual(values = pos_colors) +
  labs(
    title    = "Age vs log(Transfer Fee) by Position — Peak Value Age",
    subtitle = "Each position shows different peak transfer value age",
    x        = "Age at Transfer",
    y        = "log(Transfer Fee)",
    color    = "Position Group"
  ) +
  theme_minimal(base_size = 11)

p8a + p8b
```

---

## Graph 9. Correlation Matrix

```{r fig.width=11, fig.height=11, message=FALSE, warning=FALSE}
corr_vars <- clean_data %>%
  select(
    log_transfer_fee,
    age_at_transfer,
    contract_years_remaining,
    UEFA_coeff_from,
    xG_Per, xAG_Per, `npxG+xAG_Per`,
    Gls_per90, Ast_per90,
    PrgC_per90, Succ_Take_per90,
    Tkl_per90, Won_percent_Aerial
  ) %>%
  drop_na()

corr_matrix <- cor(corr_vars)

corrplot(corr_matrix,
         method      = "color",
         type        = "upper",
         tl.cex      = 0.85,
         tl.col      = "black",
         addCoef.col = "black",
         number.cex  = 0.65,
         col         = colorRampPalette(
           c("#e6550d", "white", "#3182bd"))(200),
         title       = "Correlation Matrix — Key Variables",
         mar         = c(0, 0, 2, 0))
```

---

## Graph 10. Position-Specific Key Metrics vs log(Transfer Fee)

```{r fig.width=14, fig.height=10, message=FALSE, warning=FALSE}
p_fw <- ggplot(
  clean_data %>% filter(pos_group == "FW"),
  aes(x = `npxG+xAG_Per`, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#e6550d") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "FW: npxG+xAG per 90 vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "FW"),
                         " | non-penalty xG + xA"),
       x = "npxG+xAG per 90", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

p_am <- ggplot(
  clean_data %>% filter(pos_group == "AM"),
  aes(x = xAG_Per, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#fd8d3c") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "AM: xAG per 90 vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "AM"),
                         " | expected assists"),
       x = "xAG per 90", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

p_cm <- ggplot(
  clean_data %>% filter(pos_group == "CM/DM"),
  aes(x = Cmp_percent_Total, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#3182bd") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "CM/DM: Pass Completion% vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "CM/DM"),
                         " | passing accuracy"),
       x = "Pass Completion%", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

p_cb <- ggplot(
  clean_data %>% filter(pos_group == "CB"),
  aes(x = Won_percent_Aerial, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#31a354") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "CB: Aerial Duels Won% vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "CB"),
                         " | aerial dominance"),
       x = "Aerial Duels Won%", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

p_sb <- ggplot(
  clean_data %>% filter(pos_group == "SB"),
  aes(x = PrgC_per90, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#74c476") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "SB: Progressive Carries per 90 vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "SB"),
                         " | attacking contribution"),
       x = "Progressive Carries per 90", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

p_gk <- ggplot(
  clean_data %>% filter(pos_group == "GK", !is.na(PSxG)),
  aes(x = PSxG, y = log_transfer_fee, size = age_at_transfer)
) +
  geom_point(alpha = 0.4, color = "#756bb1") +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 1) +
  scale_size_continuous(range = c(1, 4), guide = "none") +
  labs(title = "GK: PSxG vs log(Fee)",
       subtitle = paste0("n=", sum(clean_data$pos_group == "GK" &
                                    !is.na(clean_data$PSxG)),
                         " | shot-quality-adjusted saves"),
       x = "PSxG", y = "log(Transfer Fee)") +
  theme_minimal(base_size = 10)

(p_fw + p_am) / (p_cm + p_cb) / (p_sb + p_gk)
```

---

## Graph 11. Position-Level Age Peak Analysis

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
ggplot(
  clean_data %>% filter(pos_group != "Other"),
  aes(x = age_at_transfer, y = log_transfer_fee,
      color = pos_group, fill = pos_group)
) +
  geom_smooth(method = "lm", formula = y ~ x + I(x^2),
              se = TRUE, alpha = 0.1, linewidth = 1.1) +
  scale_color_manual(values = pos_colors) +
  scale_fill_manual(values = pos_colors) +
  labs(
    title    = "Age vs log(Transfer Fee) by Position — Peak Value Age",
    subtitle = "Each position shows different peak transfer value age",
    x        = "Age at Transfer",
    y        = "log(Transfer Fee)",
    color    = "Position Group",
    fill     = "Position Group"
  ) +
  theme_minimal(base_size = 12)
```

---

## Graph 12. Traditional vs Advanced Metrics — Position-Specific Comparison

```{r fig.width=14, fig.height=6, message=FALSE, warning=FALSE}
pos_metric_corr <- bind_rows(
  clean_data %>% filter(pos_group == "FW") %>%
    summarise(
      pos_group   = "FW",
      Traditional = cor(Gls_per90,      log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(`npxG+xAG_Per`, log_transfer_fee, use = "complete.obs"),
      Trad_label  = "Goals/90",
      Adv_label   = "npxG+xAG/90"
    ),
  clean_data %>% filter(pos_group == "AM") %>%
    summarise(
      pos_group   = "AM",
      Traditional = cor(Ast_per90, log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(xAG_Per,   log_transfer_fee, use = "complete.obs"),
      Trad_label  = "Assists/90",
      Adv_label   = "xAG/90"
    ),
  clean_data %>% filter(pos_group == "CM/DM") %>%
    summarise(
      pos_group   = "CM/DM",
      Traditional = cor(Ast_per90,        log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(Cmp_percent_Total, log_transfer_fee, use = "complete.obs"),
      Trad_label  = "Assists/90",
      Adv_label   = "Pass Completion%"
    ),
  clean_data %>% filter(pos_group == "CB") %>%
    summarise(
      pos_group   = "CB",
      Traditional = cor(Clr_per90,         log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(Won_percent_Aerial, log_transfer_fee, use = "complete.obs"),
      Trad_label  = "Clearances/90",
      Adv_label   = "Aerial Duels Won%"
    ),
  clean_data %>% filter(pos_group == "SB") %>%
    summarise(
      pos_group   = "SB",
      Traditional = cor(Ast_per90, log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(xAG_Per,   log_transfer_fee, use = "complete.obs"),
      Trad_label  = "Assists/90",
      Adv_label   = "xAG/90"
    ),
  clean_data %>%
    filter(pos_group == "GK", !is.na(PSxG), !is.na(GA90)) %>%
    summarise(
      pos_group   = "GK",
      Traditional = cor(GA90, log_transfer_fee, use = "complete.obs"),
      Advanced    = cor(PSxG, log_transfer_fee, use = "complete.obs"),
      Trad_label  = "GA per 90",
      Adv_label   = "PSxG"
    )
) %>%
  pivot_longer(cols = c(Traditional, Advanced),
               names_to  = "metric_type",
               values_to = "correlation")

ggplot(pos_metric_corr,
       aes(x = metric_type, y = correlation, fill = metric_type)) +
  geom_col(alpha = 0.85, width = 0.6) +
  geom_hline(yintercept = 0, linewidth = 0.5, color = "gray40") +
  geom_text(
    aes(label = round(correlation, 3),
        vjust = ifelse(correlation >= 0, -0.4, 1.2)),
    size = 3.2, fontface = "bold"
  ) +
  scale_fill_manual(values = c("Traditional" = "#3182bd",
                                "Advanced"    = "#e6550d")) +
  facet_wrap(
    ~pos_group, nrow = 2,
    labeller = labeller(pos_group = c(
      "FW"    = "FW\n(Goals vs npxG+xAG)",
      "AM"    = "AM\n(Assists vs xAG)",
      "CM/DM" = "CM/DM\n(Assists vs Pass%)",
      "CB"    = "CB\n(Clearances vs Aerial%)",
      "SB"    = "SB\n(Assists vs xAG)",
      "GK"    = "GK\n(GA90 vs PSxG)"
    ))
  ) +
  labs(
    title    = "Traditional vs Advanced Metrics: Correlation with Transfer Fee",
    subtitle = "Each position uses its own position-specific metric pair — Red bar higher = advanced metrics win",
    x        = "Metric Type",
    y        = "Correlation with log(Transfer Fee)",
    fill     = "Metric Type"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    legend.position = "top",
    strip.text      = element_text(face = "bold")
  )
```

---

## Graph 13. Age Group Transfer Fee Distribution: U21 / Prime / O30
### [v5.0 신규] 연령 구간별 3-way 비교 — U21 프리미엄 + O30 할인 시각화

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
# 연령 구간 변수 생성
clean_data <- clean_data %>%
  mutate(
    age_group = case_when(
      age_at_transfer <= 21 ~ "U21\n(≤21)",
      age_at_transfer >= 30 ~ "O30\n(≥30)",
      TRUE                  ~ "Prime\n(22-29)"
    ),
    age_group = factor(age_group,
                       levels = c("U21\n(≤21)", "Prime\n(22-29)", "O30\n(≥30)"))
  )

# 그룹별 통계 계산
age_group_stats <- clean_data %>%
  filter(!is.na(log_transfer_fee)) %>%
  group_by(age_group) %>%
  summarise(
    n              = n(),
    median_raw_fee = median(transfer_fee_raw, na.rm = TRUE),
    median_log_fee = median(log_transfer_fee, na.rm = TRUE),
    .groups        = "drop"
  )

ggplot(clean_data %>% filter(!is.na(log_transfer_fee)),
       aes(x = age_group, y = log_transfer_fee, fill = age_group)) +
  geom_boxplot(outlier.alpha = 0.3, outlier.size = 1.0,
               width = 0.55, linewidth = 0.6) +
  stat_summary(fun = mean, geom = "point", shape = 18,
               size = 3.5, color = "black", show.legend = FALSE) +
  geom_text(data = age_group_stats,
            aes(x     = age_group,
                y     = median_log_fee,
                label = paste0("Median\n€",
                               round(median_raw_fee / 1e6, 1),
                               "M\nn=", n)),
            vjust = -1.2, size = 3.2, fontface = "bold",
            inherit.aes = FALSE) +
  scale_fill_manual(values = c(
    "U21\n(≤21)"     = "#a8e6cf",
    "Prime\n(22-29)" = "#74b9ff",
    "O30\n(≥30)"     = "#ff7675"
  )) +
  labs(
    title    = "Transfer Fee Distribution by Age Group: U21, Prime, and O30 Segments",
    subtitle = "Three-way comparison — U21 premium and O30 discount as distinct market pricing tiers\nDiamond = Mean  |  Line = Median",
    x        = "Age Group",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title      = element_text(face = "bold", size = 13),
    plot.subtitle   = element_text(size = 10, color = "#555555"),
    legend.position = "none"
  )
```

---

## Graph 14. O30 Players vs Full Sample Transfer Fee Distribution
### [v5.0 신규] O30 선수 vs 전체 이적료 분포 비교 — G6(U21)과 대칭 구조

```{r fig.width=12, fig.height=6, message=FALSE, warning=FALSE}
# 박스플롯 비교 (G6 U21과 동일 구조)
p14a <- ggplot(clean_data,
               aes(x = O30_label, y = log_transfer_fee, fill = O30_label)) +
  geom_boxplot(alpha = 0.85, outlier.alpha = 0.25) +
  stat_summary(fun = mean, geom = "point", shape = 18,
               size = 3, color = "black", show.legend = FALSE) +
  scale_fill_manual(values = c("O30 (Veteran)" = "#e74c3c",
                                "Under 30"      = "#3182bd")) +
  labs(
    title    = "Transfer Fee: O30 Veteran vs Under-30 Players",
    subtitle = paste0("O30 n=", sum(clean_data$O30_dummy == 1, na.rm = TRUE),
                      "  |  Under 30 n=",
                      sum(clean_data$O30_dummy == 0, na.rm = TRUE)),
    x        = "Player Type",
    y        = "log(Transfer Fee)"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "none")

# 밀도 곡선 + 오버레이 (전체 샘플 vs O30)
full_density <- clean_data %>%
  filter(!is.na(log_transfer_fee)) %>%
  mutate(group = "Full Sample")

o30_density <- clean_data %>%
  filter(!is.na(log_transfer_fee), O30_dummy == 1) %>%
  mutate(group = "O30 Players")

density_combined <- bind_rows(full_density, o30_density)

p14b <- ggplot(density_combined,
               aes(x = log_transfer_fee, fill = group, color = group)) +
  geom_density(alpha = 0.40, linewidth = 1.0) +
  scale_fill_manual(values  = c("Full Sample"  = "#3182bd",
                                 "O30 Players" = "#e74c3c")) +
  scale_color_manual(values = c("Full Sample"  = "#2c6fad",
                                 "O30 Players" = "#c0392b")) +
  geom_vline(
    xintercept = median(clean_data$log_transfer_fee[
      clean_data$O30_dummy == 1], na.rm = TRUE),
    color = "#c0392b", linetype = "dashed", linewidth = 0.9
  ) +
  geom_vline(
    xintercept = median(clean_data$log_transfer_fee, na.rm = TRUE),
    color = "#2c6fad", linetype = "dashed", linewidth = 0.9
  ) +
  annotate("text",
           x = median(clean_data$log_transfer_fee[
             clean_data$O30_dummy == 1], na.rm = TRUE) - 0.15,
           y = 0.35,
           label = paste0("O30\nMedian\n€",
                          round(median(clean_data$transfer_fee_raw[
                            clean_data$O30_dummy == 1], na.rm = TRUE) / 1e6, 1),
                          "M"),
           color = "#c0392b", size = 3.0, hjust = 1, fontface = "bold") +
  annotate("text",
           x = median(clean_data$log_transfer_fee, na.rm = TRUE) + 0.15,
           y = 0.35,
           label = paste0("Full\nMedian\n€",
                          round(median(clean_data$transfer_fee_raw,
                                       na.rm = TRUE) / 1e6, 1),
                          "M"),
           color = "#2c6fad", size = 3.0, hjust = 0, fontface = "bold") +
  labs(
    title    = "Transfer Fee Density: O30 Players vs Full Sample",
    subtitle = "Red = O30 veterans  |  Blue = Full dataset  |  Dashed lines = respective medians",
    x        = "log(Transfer Fee)",
    y        = "Density",
    fill     = "Group",
    color    = "Group"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "top")

p14a + p14b
```
